Strict Pure Functional Programming and Automatic Parallelization\\ (New-project-in-progess Paper)

### 2016-03-16 pubs/tfp16/paper.tex
Start of the testing section

>>>>

We have developed a extensive test suite using the CMake \cite{cmake-book}
CTest tool. The full test suite is automatically run and any failures reported
using a Jenkins continuous integration server \cite{jenkins-book}. There are
test programs for both STG and mini-Haskell. We also run each test with various
levels of garbage collection enabled.

The test suite is partitioned into a number of directories which control what
testing is done for a specific program. Given our goal of exploring various
levels of strictness, most tests are run with all evaluation strategies (3
degrees of function strictness by two degrees of constructor strictness).
One interesting class of test programs are those which require non-strict
semantics. For these programs we test not only that the test leads to the expected
result with non-strict semantics, but also that the program returns a
"blackhole" in the case of strict semantics. Another important class of test
programs are those which should fail with a known error (e.g. a parsing error)
for these programs the test suite checks the output against an expected error
regular expression.
